Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-07-07 eg6-letters/long-paper/prc-dvcshelium.tex
add tables for the coherent and incoherent alu (90)
Implement all minor changes

\begin{abstract}
Measurements of the beam-spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) are 
reported. A 6 GeV longitudinally polarized electron beam was incident on a 
pressurized $^4$He gaseous target to study the partonic structure of the 
nucleus and the bound nucleons. To ensure the exclusivity of the reactions, 
CLAS was upgraded with a radial time projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance at forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developments with three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
parton distributions (GPD) and transverse momentum dependent parton distribution functions (PDF)
can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
of the nucleus with an original perspective~\cite{Dupre:2015jha}. This new approach is 
particularly needed as the quark structure of the nucleus remains today the subject of numerous
controversies. Indeed, while much progress has been made in measuring the nuclear
PDFs, their shape remains fundamentally unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the GPDs can be probed conveniently through the measurement of the
spin asymmetries generated by the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
production of a photon limits the possibilities of final state interactions in the nuclear 
medium and offers a unique opportunity to make a measurement free of final state interactions 
(FSI). Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
is significantly simplified with the reduction to a single GPD intervening in the process at leading order. The 
measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
the HERMES collaboration \cite{Airapetian:2009cga} lead to controversial conclusions. We present here
in detail the more recent measurements from the CLAS collaboration, which has been already partially presented
in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the CLAS nuclear DVCS experiment, detail the methods used for the
data analysis and produce the complete experimental results for each channel measured.

@@

The different spin states possible lead to several independent GPDs for any 
given hadron. The proper accounting of the number of GPDs must be done with 
regard to the symmetries of the system. At leading order and leading twist, we 
find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will have two GPDs, 
for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
parton helicity flip, they are called transversity GPDs and do not intervene 
in the DVCS process.

DVCS is the main experimental probe of the GPDs. However, this process does not allow
for an extraction of the GPDs in full phase space parameters. Instead, DVCS gives access
to the GPDs integrated over $x$, in the following form:
\begin{equation}
	\int^1 _{-1} dx F^{q}(x,\xi,t) \left [ {1 \over x - \xi - i \epsilon} 
	                                   \mp {1 \over x + \xi - i \epsilon} \right]. 
\end{equation}
To account for this and simplify equations, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
    \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
quark flavors.

Experimentally, another process is indistinguishable from the DVCS, the Bethe-Heitler (BH) 
process in which 
the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
photon-hadron interaction is the same as in elastic scattering and depends on the
target form factors rather than its GPDs. The DVCS and BH processes are experimentally 
indistinguishable as they
have identical final states, such that they interfere in the squared amplitude of the
exclusive photo-production process:
\begin{equation}
|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms increase significantly the cross section in specific parts of the phase space
and lead to significant beam spin asymmetries (BSA), which are the focus of the measurements presented 
here.

@@

This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$ of the 
spin-0 nucleus. The 
$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
These factors have the following simplified expressions:
\begin{eqnarray}
	\label{eq:alpha1}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
	\label{eq:alpha4}
\end{eqnarray}
where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
Appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.

@@

An important issue with the use of this theoretical framework is the large mass of the 
helium nuclei. Recent work indicate that the effect of this correction is moderate 
\cite{Braun:2012bg}, however the applicability to such a large mass remains to be
fully explored from the theoretical point of view.

@@

The first measurement of nuclear DVCS has been performed by the HERMES 
collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
nuclear targets and looked at the $A$ dependence of the
BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large error bars, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

\begin{figure}[tbp!]
\center
	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
	for a series of nuclei \cite{Airapetian:2009cga}.}
\label{fig:HERMES1}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
\caption{The sinus moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
	\cite{Airapetian:2009cga}.}
\label{fig:HERMES2}
\end{figure}

@@

Altogether, large error bars and the failure to properly separate the coherent and 
incoherent channels have strongly impaired the measurement and any conclusions that could be
obtained from it. The CLAS experiment presented here has profited largely from this
result and was designed specifically to solve these two issues of low statistics and exclusivity.

@@

The CLAS experiment had for main objective to explore the coherent DVCS on helium-4 and assess if
the predicted BSA increase could be observed and if GPDs could be extracted from it. In order to
perform this measurement however, several instrumentation challenges needed to be resolved. First, to
measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
radial time projection chamber (RTPC) was installed to measure the
helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
will review the important elements of this detection setup.

@@

The CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
accelerator facility (CEBAF). CLAS is specifically designed to study the multi-particles final states
that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement. CLAS is composed of six identical radial 
sectors separated by coils of toroidal magnets, with each sector made of four detectors 
as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
are placed between the torus magnet to reconstruct the charge particle's tracks and 
calculate their momentum. An array of scintillators is placed behind drift chambers to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
In forward region, from 8 to 45 degree, these two detectors are complimented with 
Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
important for electron identification.

@@

Altogether, CLAS provides a large acceptance of about $2\pi$ steradians for momenta 
starting at 200 MeV/c. During the nuclear DVCS experiment,
the beam energy was highest for CLAS with 6.064 GeV, while the beam intensity varied
between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
During the experiment, the data acquisition rate ran around 3 kHz with about 70\% live-time
using an inclusive electron trigger.

@@

The CLAS collaboration has established a specific setup to measure the typically 
small angle photons of the DVCS process. This setup is composed of an inner 
calorimeter and a solenoid and has lead to numerous DVCS measurements on proton 
targets \cite{Seder:2014cdc,Jo:2015ema,HirlingerSaylor:2018bnu}.

@@

The photons from DVCS are mainly detected with the inner calorimeter. No specific 
identification cuts are used in this detector as large energy deposit are dominantly 
from electrons and photons, which cannot be separated reliably. However, the detection 
of an electron at larger angle in CLAS 
highly suppresses the number of electrons in the calorimeter, moreover
the exclusivity cuts used later in the analysis further this suppression. Left over accidentals, will be
accounted for in the background subtraction. The inner calorimeter was calibrated through a series
of steps, involving the reconstruction of $\pi^0$ from their two photons decay. Calibration was obtained 
with an iterative process to adjust each crystal gain to obtain the most accurate $\pi^0$ mass. A
global calibration of the calorimeter was also performed to account for incident angle, energy and 
time dependent effects.

@@

To select exclusive events and suppress the backgrounds, we define several 
exclusivity cuts based on energy and momentum conservation. In principle, 
a selection based on two or three variables can be used to guaranty the 
exclusivity of the process. However, in such experiment, where particles 
are detected at very different energies and with very different detector 
resolutions, we chose to over constrain the selection by using seven 
variables. The seven variables are defined as follow for the coherent 
DVCS (replace helium by proton for the incoherent case):
\begin{itemize}
	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
		the recoil helium, defined as the angle between the helium, virtual photon
		plane and the virtual photon, real photon plane;
	\item Missing energy of the full system;
	\item Missing mass of the full system;
	\item Missing transverse momentum of the full system;
	\item Missing mass of the system electron-helium;
	\item Missing mass of the system electron-photon;
	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
		electron-helium system.
\end{itemize}

In the analysis, we apply selection cuts based on a fit of the exclusive peak at 3$\sigma$ around 
the mean value for each variable. This systematic method helps to avoid any bias 
in the selection of the events. The selection of coherent DVCS with these variables is illustrated in 
Fig. \ref{fig:CohExcCuts}. We note on these distributions only few minor anomalies, where the 
distribution have some asymmetries. These are linked with the detector resolutions, that impact
some of the kinematic variables non linearly. The selection of incoherent DVCS is presented in 
Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
offset distributions. The larger distributions are largely attributed to the effect of 
Fermi motion, but simulations have shown that this effect is not strong enough to fully 
reproduce the distribution widths and final state interactions must play a role as well. 
The offsets of some distributions is caused by slight detector 
misalignment between CLAS sectors and are within the levels obtained with free proton 
targets~\cite{HirlingerSaylor:2018bnu} to which they can be directly compared.

@@

As discussed above, the best way to define $t$ in the incoherent channel is not completely
straightforward. As can be seen in the Fig. \ref{fig:InCohDiag}, 
we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
identical, but experimentally we face some issues. The measurement of $t$ is less precise than
$t^\prime$ because it involves the photon rather than charged particles. However, the 
exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
we studied the difference between the two results by analyzing the data independently using the two 
definitions. We found no significant difference between them, as it is 
illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$,
which is the correct definition with the slightly poorer resolution.

@@

In Fig. \ref{fig:CohALUphi}, we present the results for the BSA in the coherent DVCS channel. We 
observe the dominant sinusoidal component typical of the DVCS BSA, with an amplitude almost 
double than the one measured for the free proton \cite{Jo:2015ema}. This 
predicted feature of nuclear DVCS \cite{Guzey:2003jh} is observed here for the first time, we
can conclude that this measurement cleanly isolates the coherent DVCS process. The absence of 
this feature in the previous measurement from HERMES \cite{Airapetian:2009cga} and its clear observation here indicates that the recoil 
detection is a necessity to isolate the effects of the coherent DVCS process from backgrounds.

@@

\begin{figure}[tbp]
\center
\includegraphics[width=17cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles \cite{Airapetian:2009cga}. Theoretical predictions 
	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, while the calculation from Fucini 
	{\it et al.}~\cite{Fucini:2018gso} is shown with a magenta long dash line.}
\label{fig:CohALU90}
\end{figure}

We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model compared to the 
data~\cite{Liuti:2005gi} is based on the hypothesis that the main nuclear effects are 
included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
appears that this model undershoots the results systematically. However, a new independent 
calculation \cite{Fucini:2018gso}, using similar principles but with a non diagonal nuclear spectral 
function \cite{Viviani:2001wu} based on the Av18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
well. Another factor in the difference is that the recent calculation from Fucini {\it et 
al.}~\cite{Fucini:2018gso} benefited from using the precise kinematic of each points presented 
in appendix \ref{sec:fullresults}. Including this information appears to have a significant 
impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
which is well reproduced when using this information.

>>>>

\begin{abstract}
We report on the measurement of the beam-spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) at
Jefferson Lab using a 6 GeV longitudinally polarized electron beam incident on a 
pressurized $^4$He gaseous target. We detail the method used to ensure the exclusivity 
of the measured reactions, in particular the upgrade of CLAS with a radial time 
projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance at forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developments with three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
parton distributions (GPD) and transverse momentum dependent parton distribution functions (TMD)
can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
of the nucleus with an original perspective~\cite{Dupre:2015jha}. This new approach is 
particularly needed as the quark structure of the nucleus remains today the subject of numerous
controversies. Indeed, while much progress has been made in measuring the nuclear
parton distribution functions, their shape remains fundamentally 
unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the GPDs can be probed conveniently through the measurement of the
spin asymmetries generated by the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
production of a photon limits the possibilities of final state interactions in the nuclear 
medium and offers a unique opportunity to make a measurement free of final state interactions 
(FSI). Moreover, with a spin-0 nuclear target, the extraction of the GPD from the DVCS data 
is significantly simplified since a single GPD is occurring in the process at leading order. However, the 
measurement of the nuclear DVCS is challenging experimentally and the first attempts by 
the HERMES collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
in detail the more recent measurements by the CLAS collaboration, which has been already partially presented
in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the CLAS nuclear DVCS experiment, detail the methods used for the
data analysis and produce the complete experimental results for each channel measured.

@@

The different possible spin states lead to several independent GPDs for any 
given hadron. The proper accounting of the number of GPDs must be done with 
regard to the symmetries of the system. At leading order and leading twist, we 
find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will have two GPDs, 
for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
parton helicity flip, they are called transversity GPDs and do not intervene 
in the DVCS process.

DVCS is the main experimental probe of the GPDs. However, this process does not allow
for an extraction of the GPDs in the full phase space of parameters. Instead, DVCS gives access
to the GPDs integrated over $x$. 
To account for this and simplify equations, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
    \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe does not differentiate
quark flavors.

Experimentally, another process is indistinguishable from DVCS, the Bethe-Heitler (BH) 
process in which 
the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
photon-hadron interaction is the same as in elastic scattering and depends on the
target form factors rather than its GPDs. The DVCS and BH processes are experimentally 
indistinguishable as they
have identical final states, such that they interfere in the squared amplitude of the
exclusive photo-production process:
\begin{equation}
|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms increase significantly the cross section in specific parts of the phase space
and lead to significant beam spin asymmetries (BSA), which are the focus of the measurements presented 
here.

@@

This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$ of the 
spin-0 nucleus. The 
$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
These factors have the following simplified expressions:
\begin{eqnarray}
	\label{eq:alpha1}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
	\label{eq:alpha4}
\end{eqnarray}
where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
Appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.

@@

An important issue with the use of this theoretical framework is the large mass of the 
helium nucleus. Recent work indicate that the effect of this correction is moderate 
\cite{Braun:2012bg}, however the applicability to such a large mass remains to be
fully explored from the theoretical point of view.

@@

The first measurement of nuclear DVCS has been performed by the HERMES 
collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
nuclear targets and looked at the $A$ dependence of the
BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large uncertainties, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

\begin{figure}[tbp!]
\center
	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
	for a series of nuclei \cite{Airapetian:2009cga}, gray bands represent the systematic 
        uncertainties.}
\label{fig:HERMES1}
\end{figure}

\begin{figure}[tbp!]
\center
\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
\caption{The sinus moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
the outer represent the quadratic sum of the statistical and systematic uncertainties.}
\label{fig:HERMES2}
\end{figure}

@@

Altogether, large error bars and the failure to properly separate the coherent and 
incoherent channels have strongly impaired the interpretation of the measurement 
and the conclusions that could be
obtained from it. The CLAS experiment presented here has profited largely from this
result and was designed specifically to solve these two issues of low statistics and exclusivity.

@@

The CLAS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
perform this measurement however, several instrumentation challenges needed to be resolved. First, to
measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
radial time projection chamber (RTPC) was installed to measure the
helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
will review the important elements of this detection setup.

@@

CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
accelerator facility (CEBAF). CLAS is specifically designed to study the multi-particles final states
that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
configurations made it an ideal place for this new DVCS measurement. CLAS is composed of six identical radial 
sectors separated by coils of toroidal magnets, with each sector made of four detectors 
as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
are placed between the torus magnet to reconstruct the charged particles' tracks and 
calculate their momentum. An array of scintillators is placed behind the drift chambers to measure 
a precise time for each track and perform time-of-flight measurement 
\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
In forward region, from 8 to 45 degree, these two detectors are complemented with 
Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
important for electron identification.

@@

Altogether, CLAS provides a large acceptance of about $2\pi$ steradians for momenta 
starting at 200 MeV/c. During the nuclear DVCS experiment,
the beam energy was highest for CLAS with 6.064 GeV, while the beam intensity varied
between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
During the experiment, the data acquisition operated at a rate of about 3 kHz with about 70\% live-time
using an inclusive electron trigger.

@@

The CLAS collaboration has established a specific setup to measure the typically 
small angle photons of the DVCS process. This setup is composed of an inner 
calorimeter and a solenoid and has been employed for numerous DVCS measurements on proton 
targets \cite{Seder:2014cdc,Jo:2015ema,HirlingerSaylor:2018bnu}.

@@

The photons from DVCS are mainly detected with the inner calorimeter. No specific 
identification cuts are used in this detector as large energy deposit are dominantly 
from electrons and photons, which cannot be separated reliably. However, the detection 
of an electron at larger angle in CLAS highly suppresses the number of electrons 
in the calorimeter, moreover the exclusivity cuts used later in the analysis further 
this suppression. Left over accidentals are accounted for in the background subtraction 
described below. The inner calorimeter was calibrated through a series of steps, 
involving the reconstruction of $\pi^0$ from their decay into two photons. Calibration was obtained 
with an iterative process to adjust each crystal gain to obtain the most accurate $\pi^0$ mass. A
global calibration of the calorimeter was also performed to account for incident angle, energy and 
time dependent effects.

@@

To select exclusive events and suppress the backgrounds, we define several 
exclusivity cuts based on energy and momentum conservation. In principle, 
a selection based on two or three variables can be used to guarantee the 
exclusivity of the process. However, in such experiment, where particles 
are detected at very different energies and with very different detector 
resolutions, we chose to over constrain the selection by using seven 
variables. The seven variables are defined as follow for the coherent 
DVCS (replace helium by proton for the incoherent case):
\begin{itemize}
	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
		the recoil helium, defined as the angle between the helium, virtual photon
		plane and the virtual photon, real photon plane;
	\item Missing energy of the full system;
	\item Missing mass of the full system;
	\item Missing transverse momentum of the full system;
	\item Missing mass of the electron-helium system;
	\item Missing mass of the electron-photon system;
	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
		electron-helium system.
\end{itemize}

In the analysis, we apply selection cuts based on a fit of the exclusive peak at 3$\sigma$ around 
the mean value for each variable. This systematic method helps to avoid any bias 
in the selection of the events. The selection of coherent DVCS with these variables is illustrated in 
Fig. \ref{fig:CohExcCuts}. We note on these distributions only few minor anomalies, where the 
distribution have some asymmetries. These are linked with the detector resolutions, that impact
some of the kinematic variables non linearly. The selection of incoherent DVCS is presented in 
Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
offset distributions. The larger distributions are mainly attributed to the effect of 
Fermi motion, but simulations have shown that this effect is not strong enough to fully 
reproduce the distribution widths and final state interactions must play a role as well. 
The offsets of some distributions is caused by slight detector 
misalignment between CLAS sectors and are within the levels obtained with free proton 
targets~\cite{HirlingerSaylor:2018bnu} to which they can be directly compared.

@@

As discussed above, the best way to define $t$ in the incoherent channel is not completely
straightforward. As can be seen in Fig. \ref{fig:InCohDiag}, 
we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
identical, but experimentally we face some issues. The measurement of $t$ is less precise than
$t^\prime$ because it involves the photon rather than charged particles. However, the 
exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
we studied the difference between the two results by analyzing the data independently using the two 
definitions. We found no significant difference between them, as it is 
illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$,
which is the correct definition with the slightly poorer resolution.

@@

In Fig. \ref{fig:CohALUphi}, we present the results for the BSA in the coherent DVCS channel. We 
observe the dominant sinusoidal component typical of the DVCS BSA, with an amplitude almost 
double than the one measured for the free proton \cite{Jo:2015ema}. This 
predicted feature of nuclear DVCS \cite{Guzey:2003jh} is observed here for the first time, we
can conclude that this measurement cleanly isolates the coherent DVCS process. The absence of 
this feature in the previous measurement by HERMES \cite{Airapetian:2009cga} and its clear observation here indicates that the recoil 
detection is necessary to isolate the effects of the coherent DVCS process from backgrounds.

@@

\begin{figure}[tbp]
\center
\includegraphics[width=17cm]{fig3/Coherent_ALU_phi_90.pdf}
\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
	Our results are shown with black squares, HERMES results 
	with green circles \cite{Airapetian:2009cga}. Theoretical predictions 
	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
	with red full line and dashed blue, while the calculation by Fucini 
	{\it et al.}~\cite{Fucini:2018gso} is shown with a magenta long dash line.}
\label{fig:CohALU90}
\end{figure}

We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model compared to the 
data~\cite{Liuti:2005gi} is based on the hypothesis that the main nuclear effects are 
included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
appears that this model undershoots the results systematically. However, a new independent 
calculation \cite{Fucini:2018gso}, using similar principles but with a non diagonal nuclear spectral 
function \cite{Viviani:2001wu} based on the Av18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
well. Another factor in the difference is that the recent calculation by Fucini {\it et 
al.}~\cite{Fucini:2018gso} benefited from using the precise kinematic of each points presented 
in appendix \ref{sec:fullresults}. Including this information appears to have a significant 
impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
which is well reproduced when using this information.

One of the motivation for the choice of helium-4 for the coherent DVCS measurement was
a simplified extraction of the CFF $\mathcal{H}_A$ from
data. To perform this step, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data in Fig. 
\ref{fig:CohALUphi}. We present in Fig. \ref{fig:CohCFF} the real and imaginary parts 
of the single CFF of the helium-4 nucleus extracted. The results are rather encouraging, the two parts
of the CFF are constrained by data without the need of any model assumption. This capacity to obtain a
model independent result with such a limited data set offers a striking contrast with the
situation of the free proton fits \cite{Dupre:2016mai,Dupre:2017hfs}.
